Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-26 paper/paper.tex
spellchecked with GB dictionary

    We show that a probabilistic functional language can be
    implemented efficiently and integrated tightly with a
    conventional functional language with only moderate
    computational overhead. We also demonstrate how advanced
    probabilistic modeling concepts are mapped naturally
    to the functional foundation.
\end{abstract}

@@

A (almost-surely terminating) probabilistic program defines a probability distribution 
over finite feasible traces $\pmb{x}$ with probability density 
$\pi(\pmb{x}) := \gamma(\pmb{x}) / Z$ where 
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j})
  \quad \mbox{for the image $\pmb{y}$ of $\pmb{x}$}, 
  \label{eqn:p-trace}
\end{align}
and $Z$ is the normalization constant $Z := \int \gamma(\pmb{x})d(\pmb{x})$. The integral and the density use the default measure obtained by the standard extension of
a $\sigma$-finite measure on finite traces where the $\sigma$-finite measure itself is defined by
a countable sum of Lebesque and counting measures.

>>>>

    We show that a probabilistic functional language can be
    implemented efficiently and integrated tightly with a
    conventional functional language with only moderate
    computational overhead. We also demonstrate how advanced
    probabilistic modelling concepts are mapped naturally
    to the functional foundation.
\end{abstract}

@@

A (almost-surely terminating) probabilistic program defines a probability distribution 
over finite feasible traces $\pmb{x}$ with probability density 
$\pi(\pmb{x}) := \gamma(\pmb{x}) / Z$ where 
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j})
  \quad \mbox{for the image $\pmb{y}$ of $\pmb{x}$}, 
  \label{eqn:p-trace}
\end{align}
and $Z$ is the normalization constant $Z := \int \gamma(\pmb{x})d(\pmb{x})$. The integral and the density use the default measure obtained by the standard extension of
a $\sigma$-finite measure on finite traces where the $\sigma$-finite measure itself is defined by
a countable sum of Lebesgue and counting measures.
